Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-04-22 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
small updates related to the CHARMM-UA

\subsection{Simulated systems}
All simulations are ran with a standard setup for a planar lipid bilayer in zero tension and constant temperature
with periodic boundary conditions in all directions by using the GROMACS software package~\cite{hess08} 
(version numbers 4.5.X--4.6.X), LAMMPS~\cite{plimpton95} or MDynaMix~\cite{Lyubartsev00}.
The number of molecules, simulation temperatures and the length of simulations of all the simulated systems 
are listed in Tables~\ref{systems},~\ref{systemsDEHYD} and~\ref{systemsCHOL}. Full simulation
details are given in the Supplementary Information (SI) or in the original publications in case the
data is used previously therein. Additionally, the files related to the simulations and the resulting trajectories are publicly
available for almost all systems in the Zenodo collection \url{https://zenodo.org/collection/user-nmrlipids}. 
The references pointing to simulation details and files are also listed in Tables~\ref{systems},~\ref{systemsDEHYD} and~\ref{systemsCHOL}.

@@

Lee-CHARMM36-UA~\cite{henin08,lee14}     & DPPC   & 72  & 2189  & 323 & 70 & 50 & ? & SI \\
Botan-CHARMM36-UA   & DLPC   & 128  & 3840  & 323 & 30 & 20 & [\citenum{charmmUAfiles}] & SI \\

@@

NAMD was developed by the Theoretical and Computational Biophysics Group in the
 Beckman Institute for Advanced Science and Technology at the University
 of Illinois at Urbana-Champaign\cite{namd}.

@@

The distribution into all-atom  (AA) and united-atom (UA) parts within the lipids is the same
as in the original CHARMM27-UA model by H\'enin et al.~\cite{henin08}.  
This distribution differs from the one by Lee-C36-UA because  in Botan's model, C22 and C32  a
nd their hydrogens are merged into  united atoms, whereas in Lee's model their hydrogens are described explicitely.
The  united-atom Berger model ~\cite{berger97} was used for the tails and the UA-AA interactions as in Ref. ~\citenum{henin08}. 
The difference between this model and the original oneby H\'enin~\cite{henin08} is the replacement of the 
AA parameters for the heads by  the parameters of the all-atom
 CHARMM36 force-field~\cite{klauda10}. Contrarily to the model by Lee et al.~\cite{lee14}, no reparametrization was done.

>>>>

\subsection{Simulated systems}
All simulations are ran with a standard setup for a planar lipid bilayer in zero tension and constant temperature
with periodic boundary conditions in all directions by using the GROMACS software package~\cite{hess08} 
(version numbers 4.5.X--4.6.X), LAMMPS~\cite{plimpton95}, MDynaMix~\cite{Lyubartsev00} or NAMD~\cite{phillips05}.
The number of molecules, simulation temperatures and the length of simulations of all the simulated systems 
are listed in Tables~\ref{systems},~\ref{systemsDEHYD} and~\ref{systemsCHOL}. Full simulation
details are given in the Supplementary Information (SI) or in the original publications in case the
data is used previously therein. Additionally, the files related to the simulations and the resulting trajectories are publicly
available for almost all systems in the Zenodo collection \url{https://zenodo.org/collection/user-nmrlipids}. 
The references pointing to simulation details and files are also listed in Tables~\ref{systems},~\ref{systemsDEHYD} and~\ref{systemsCHOL}.

@@

Lee-CHARMM36-UA~\cite{lee14}     & DPPC   & 72  & 2189  & 323 & 70 & 50 & ? & SI \\
Botan-CHARMM36-UA~\cite{henin08}   & DLPC   & 128  & 3840  & 323 & 30 & 20 & [\citenum{charmmUAfiles}] & SI \\

@@

NAMD was developed by the Theoretical and Computational Biophysics Group in the
 Beckman Institute for Advanced Science and Technology at the University
 of Illinois at Urbana-Champaign\cite{phillips05}.

@@

The distribution into all-atom  (AA) and united-atom (UA) parts within the lipids is the same
as in the original CHARMM27-UA model by H\'enin et al.~\cite{henin08}.  
This distribution differs from the one by Lee-C36-UA because  in Botan's model, C22 and C32 and 
their hydrogens are merged into  united atoms, whereas in Lee's model their hydrogens are described explicitely.
The  united-atom Berger model ~\cite{berger97} was used for the tails and the UA-AA interactions as in Ref. ~\citenum{henin08}. 
The difference between this model and the original one by H\'enin~\cite{henin08} is the replacement of the 
AA parameters for the heads by  the parameters of the all-atom
 CHARMM36 force-field~\cite{klauda10}. Contrarily to the model by Lee et al.~\cite{lee14}, no reparametrization was done.
